\chapter{Marketing}

\section{Social Media}

Due to the popularity of social media and its ability to bring people with similar interests together, \ourteam{} has created a number of social media accounts to connect with their target audience, providing a look at the game's development.

\subsection{Tumblr}
Every week, a member of \ourteam{} will write a post on the team's Tumblr blog incorporating figures and images from the development process. This post will describe what aspects of the game the team is currently working on, and discuss upcoming features and plans. Through this account, \ourteam{} also hopes to follow and connect with other game developers and development teams.

\subsection{Twitter}
Twitter will be used to share short announcements pertaining to \ourteam{}. Announcements can include reaching large milestones for \ourgame{}, as well as side projects and events the team is participating in. The Twitter account can repost relevant tweets that individual members have posted to their own Twitter accounts. Gameplay and development videos created with the Vine app can also be posted. In the future, it can be used as a way to directly communicate and exchange ideas with the userbase of \ourgame{}.

\section{Live Events}
\ourteam{} will be participating in various game jams throughout the year to hone their development skills and to grow together as a team. At these events, they will have the opportunity to show off \ourengine{} to generate interest. Members of \ourteam{} will also attend local developer meet-ups, such as Dirty Rectangles, to network and discuss game development.

\section{Website}
In preparation for the Senior Project fair, a promotional website will be created by members of \ourteam{}. This website will include an overview of the game's story, mechanics, and features. The site will include a trailer for \ourgame{} and list each member of the team alongside their roles.

\section{Promotional Materials}
Game and engine posters will be designed and posted to promote the game's unveiling at the 2016 IMD Senior project fair. Additionally, candies reminiscent of \ourteam{}'s logo will be provided.