\section{Generative Audio}
The soundtrack for \ourgame{} will feature a number of original upbeat dance tracks and thumping rock songs to match the party theme. Additionally, various sound effects will be created for different aspects of \ourgame{}. Navigational sound effects such as footsteps, doors opening, and collisions will be added to enhance the atmosphere of the game. Sound effects will also be created to increase the excitement of the yelling contests. These will include audience sound effects such as cheering and failure sound effects for the player's actions. 

\subsection{Generative Speech}
As \ourteam{} plans to include a prohibitively large amount of written content, full voice-overs will not be possible. Instead, \ourgame{} will implement a generative audio system in order to simulate speech. Characters will be randomly assigned an individual voice sample which will be the basis for all of their audio. The audio system will detect the letters used when a character is speaking and convert the ASCII character code into a pitch shift applied to their voice sample. In addition to automatically providing audio for written content, using this system will allow \ourteam{} to generate aspects of the character dialogue without sacrificing the audio component.

\subsection{Generative Music}
\label{sec:audio_generation}
An audio clip of each note in an octave will be recorded and used for procedurally generating music. When a song is created, a scale will be chosen, dictating which notes can  be used in a song. The notes can then be pitch shifted by octaves if desired. A time signature will also be chosen to effect the pacing of the song. The scale and time signature are dependent on the context of the room they will be placed in, taking into account the type of the room, and possible interactions within. To create more complex songs, songs with the same time signature but different scales can be layered along with simple percussion tracks. Multiple instruments will be recorded to add variety to the music that is able to be created.