\section{Main Plot}
\label{sec:mainplot}
The game begins at the player's desk. Ballpoint pens and other trinkets cover the surface. In the centre of the desk lies an envelope with a elaborate wax seal. The player opens the letter and finds an invitation to a party, courtesy of one Omar Clean. The player arrives at the party and hands their invitation to the mansion's kindly old butler, who leads them through the anteroom into the main part of the house. There, the player is greeted by the party's host, the mysterious Omar Clean. Omar is almost immediately bludgeoned to death by an unknown assailant, who then knocks the player unconscious.

The player awakes to find a private investigator named Goodsee Beauregard. Beauregard interrogates the player about the murder, and explains that she has spent several weeks investigating Omar Clean for suspicious behaviour. She asks the player to help her track down Omar's killer and find some answers. The player can ignore her and attend the party like nothing ever happened... but if they choose to help, the quest to unlock the mysteries of the house begins.

The player begins searching the house for the murderer, asking other party-goers for any information they have to spare and finding clues. Their investigation leads them to a secret room, where they finds the murderer standing in front of a giant electronic machine. A bright flash blinds the player. After regaining their sight, they find themselves once again outside of the house.

The player re-enters the mansion and retraces their steps from their first arrival. The butler's behaviour and the anteroom are all identical. Once the player enters the mansion, however, they find the layout of the house, its furniture, and the party-goers to be different. The player meets Omar Clean, very much alive, and very much a different person than the murder victim. The player discovers that the mysterious machine transported them to an alternate dimension. They proceed to travel between dimensions to solve the mystery of Omar Clean, and to find a way back home.

The player travels through multiple universes, meeting new friends and new versions of Omar. After several adventures, they stumble upon a house that is different from all the others. There is no party. The house looks decrepit and unkempt, and there are no guests at all. Amid the wreckage, the player finds the machine from before. Above it sits a giant portrait of a man who looks like he has been dead for many years. A voice comes from within the painting and introduces itself as Omar Clean. He tells the player how he was trapped in the painting by the Omars of other dimensions, forced to take on their weaknesses as they live their lives free of pain and death. The murderer appears and confronts the player, revealing himself to be another version of Omar Clean. He tells the player that the painting is lying -- the Omar in the painting tried to steal the life-force from all the other Omars, but ended up absorbing their weakness. He sealed himself inside the painting to preserve his body in the hopes that someone would rescue him and allow him to re-enact his plan. The "murderer" Omar explains that he travels between dimensions to protect the painting from harm. If the painting is destroyed, the weaknesses within are returned to their respective Omars, who will all die from the strain.

The player can decide to trust the Painting Omar, trust the Protector Omar, or destroy the painting. If they choose to side with Painting Omar, he regains his human form and kills the other Omar. He tells the player he will kill the other Omars and rule over all dimensions. Painting Omar activates the interdimensional transportation device, and the player sees a bright flash of white light. The game ends.

If the player trusts the Protector Omar, he thanks the player and activates the interdimensional transportation device, taking the player back to their own dimension. The party there continues on into the night as if nothing happened at all.

If the player destroys the painting, Painting Omar dies. Protector Omar curses at the player as his body splits apart and collapses to the ground. The player can then activate the machine and return to their dimension, where the party is somehow still going on. People dance, Goodsee searches for Omar, and everything seems to be the same as when the player started. The guests still whisper to each other about the reclusive Omar Clean, wondering if they will ever get a chance to meet him in person.