\chapter{The World of \ourgame{}}
\input{StorySetting_Setting}
\input{StorySetting_MainStory}
\input{StorySetting_MiddleStory}


\clearpage
\section{Characters}

\subsection{Main Characters}
Main characters are those directly related to the main storyline described in Section~\ref{sec:mainplot}. This includes Goodsee Beauregard, the Protector version of Omar Clean, and the Portrait version of Omar Clean. These characters can also be found in Appendix~\ref{app:characters}.

\character{chara_reed}
{Goodsee Beauregard, P.I.}
{Main Character}
{No-nonsense, Inquisitive, Jittery}
{Beauregard has been investigating the mysterious Omar Clean for her own purposes. When Omar Clean is murdered, she becomes obsessed with solving the murder and figuring out the mystery behind the man. And the man behind the mystery, too.}
{The player will help Beauregard determine the murderer of Omar Clean, by discovering clues and interrogating party guests.}

\character{chara_portrait_omar}
{Omar "The Portrait" Clean}
{Main Character}
{Power-hungry, Devious, Intelligent}
{Omar Clean is a scientist. He discovered a way to explore multiple dimensions and meet other versions of himself that pursued different paths in life. He decides to steal the skills and powers of these alternate versions of himself to become all-powerful. His plan backfires and he steals all the weaknesses of his alternate selves, which ages and damages him. He manages to preserve himself inside a portrait before his body is completely destroyed.}
{He wants the player to fix his machine so he can reverse the damage done to him and allow him to return to his physical form.}

\character{chara_protector_omar}
{Omar "The Protector" Clean}
{Main Character}
{Intelligent, Virtuous}
{The Protector is the version of Omar Clean from the initial universe the player explores. He is a scientist who discovers a way to explore alternate universes. He finds out that another Omar Clean (The Portrait) was trying to harness the power of other versions of Omar Cleans from throughout the multiverse. He ensures that Portrait Omar stays imprisoned and cannot hurt the other Omars.}
{He wants the player to help him keep Portrait Omar imprisoned and protect the portrait. If the portrait gets destroyed, or Portrait Omar is freed, the weaknesses of the other Omar Cleans will be restored. One of these weaknesses is aging, so if the portrait is destroyed it will mean that all versions of Omar Clean will die of old age.}

\subsection{Side Characters}
Side characters are characters that are not involved with the main storyline, but are involved in secondary storylines in \ourgame{}. These storylines are small and contained, and they resolve with help from the player. Upon completing these smaller stories, the player gets rewards that may aid them in completing the main storyline. Examples of side characters can be found in Appendix~\ref{app:characters}.

\subsection{Incidental Characters}
Many characters in \ourgame{} are simple party guests with no relation to the main storyline or any side plots. These characters will be procedurally generated using a component structure. Lines of semi-procedurally generated dialogue will be created for each character that will be said when the player interacts with the character. This use of procedural generation allows for the reuse of assets to quickly and uniquely populate each environment with interactive characters, without feeling overly repetitive for the player.