\section{User Experience Tests}
\subsection{Inventory}
The inventory system of \ourgame{} is fairly natural in relation to the real world, but there is a chance that players may not like sorting through all of the items they pick up if there are too many in their inventory. Early on, \ourteam{} will perform testing on the current design for the inventory system to determine whether it is appropriate enough for gameplay.

\subsubsection{Test Tasks}
The player will be asked to find an item in their inventory and use it on an NPC.

\subsubsection{Correct Steps}
\begin{enumerate}
\item{Face the item}
\item{Select \textbf{Pick Up} from the Item Interaction Menu}
\item{Close the Inventory Menu}
\item{Go to an NPC}
\item{Open the Inventory Menu}
\item{Equip the item (Brings up the Item Interaction Menu)}
\item{Face the NPC}
\item{Select \textbf{Use} from the Item Interaction Menu}
\end{enumerate}

\subsubsection{Metrics}
\begin{itemize}
\item{How many times did the player click the wrong button?}
\item{How many additional steps were taken?}
\end{itemize}




\subsection{Talking to Character}
The toggling speech bubble UI that \ourteam{} has designed is not very common among other game UIs, therefore  testing will be done to ensure that players can access and navigate through conversations easily.

\subsubsection{Test Tasks}
The user will be asked to talk to an NPC.

\subsubsection{Correct Steps}
\begin{enumerate}
\item{Face an NPC}
\item{Select \textbf{Talk} from Character Interaction Options Menu}
\end{enumerate}

\subsubsection{Metrics}
\begin{itemize}
\item{How long did it take for the player to reach the dialogue menu?}
\item{How long did it take for the player to select the the \textbf{Talk} option?}
\end{itemize}





\subsection{Options Menu}

\subsubsection{Test Tasks}
The user will be asked to lower the voice volume.

\subsection{Correct Steps}
\begin{enumerate}
\item{Press \textbf{Escape} key to open Main Menu}
\item{Click on \textbf{Options} button in Main Menu}
\item{Slide down voice volume control}
\end{enumerate}

\subsubsection{Metrics}
\begin{itemize}
\item{How long did it take to open the Main Menu?}
\item{How long did it take to find the Options menu}
\item{How long did it take to find and lower the volume slider?}
\end{itemize}